### 2015-03-18 ResearchNotes/Notes.Rmd
Prototyped the bootstrap loop.  Need to refine and start bootstrapping.

#Alter formula in KWH model for new variables
summary(CopyKWH)
update(CopyKWH, .~ .-TOTSQFT_EN + PSQFT, data=RECSTemp)

>>>>

#Alter formula in KWH model for new variables
formula(CopyKWH)
StructNames<-as.character(names(as.data.frame(StructProb)))
NewStruct<-paste("(",paste(unlist(StructNames),collapse="+",sep=""),")")

library(stringr)
NewForm<-str_replace_all(as.character(formula(CopyKWH)),"TOTSQFT_EN","PSQFT")
NewForm<-str_replace_all(NewForm,"StrTenure",NewStruct)
NewForm<-as.formula(paste(NewForm[2],NewForm[1],NewForm[3]))

update(CopyKWH, formula=NewForm, data=RECSTemp)

#That is one loop
#Now lets get it bootstrapping
